---
title: "Gender distribution of COVID-19"
author: "Nicolly Oliveira Santos"
format: 
  html:
    toc: true
    toc-location: body 
    code-fold: show
    code-tools: true
    df-print: paged
    embed-resources: true
  pdf: 
    toc: true
  docx: 
    toc: true
editor_options: 
  chunk_output_type: inline
editor: visual
---

```{r}
#| output: false
# Load libraries
library(here)
library(tidyverse)
library(lubridate)
install.packages("unibeCols", repos = "https://ctu-bern.r-universe.dev")
library(medicaldata)
library(unibeCols)
```

## Introduction

The aim of this study was to evaluate the distribution of confirmed cases of COVID-19 according to gender. 

## Data
15524 patients of different ages and both genders were testing for COVID-19 and the positive cases were registered.

```{r}
#| output: false
# Read data
data <- medicaldata::covid_testing
```



```{r}
# Process data
library(tidyverse)
covid_df <- data %>% select(gender, result)
covid_df
result_positive <- subset(covid_df, result == "positive")
print(result_positive)
```

@figure-cases shows the distribution of confirmed positive cases of COVID-19 according to gender.
```{r}
#| label: fig-cases
#| fig-cap: "Distribution of COVID-19 according to gender"
#| fig-width: 8
#| fig-height: 4
plot_covid <- ggplot(data = result_positive, 
                              mapping = aes(x = gender, y = result, color=gender)) + 
  geom_col(position = "stack", alpha = 0.5, fill = "white", 
           linetype = "solid", linewidth = 1.0, width = 0.5)
plot_covid
```

## Conclusions
There were more confirmed cases of COVID-19 for the female gender.
